### 2014-03-10 Docs/visualization/visualization.tex
add 2-d yt example

%-----------------------------------------------------------------------------
% yt
%-----------------------------------------------------------------------------
\section{Visualizing with \yt}
\yt is a Python package for analyzing and visualizing simulation data.
Originally \yt was written for the {\tt Enzo} code, with focus on
cosmological simulation data.  It has since been refactored to remove
the specific {\tt Enzo}isms, and now can work on various data formats,
such as the BoxLib data from \maestro\ and \castro, HDF5 data
from {\tt FLASH}, and data from the SPH code {\tt Gadget}.  For more
information, see the \yt homepage at \url{http://yt-project.org/} and
\cite{yt}.

@@

>>>>

%-----------------------------------------------------------------------------
% yt
%-----------------------------------------------------------------------------
\section{Visualizing with \yt}

\yt is a Python package for analyzing and visualizing simulation data.
Originally \yt was written for the {\tt Enzo} code, with focus on
cosmological simulation data.  It has since been refactored to remove
the specific {\tt Enzo}isms, and now can work on various data formats,
such as the BoxLib data from \maestro\ and \castro, HDF5 data
from {\tt FLASH}, and data from the SPH code {\tt Gadget}.  For more
information, see the \yt homepage at \url{http://yt-project.org/} and
\cite{yt}.

@@

\subsection{2-d datasets}

To visualize 2-d data, you can use the {\tt SlicePlot} function,
picking the normal direction to be {\tt "z"}:
\begin{lstlisting}
from yt.mods import *
 pf = load("plt00085")
s = SlicePlot(pf, "z", "tfromp")
s.save("tfromp.eps")
\end{lstlisting}
This generates the figure shown in Figure~\ref{fig:yt2d}.

\begin{figure}[!h]
\centering
\includegraphics[height=0.4\textheight]{\visfigpath/tfromp}
\caption{\label{fig:yt2d} Example slice through 3-d dataset with \yt.}
\end{figure}
